\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

%%%%%%%%%%%%
\subsection{Model Validation}

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Model Validation}\label{section:validation:results}

Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,porosity_documentation,fluidity_manual}

%,jackson_2015,pavlidis2016

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. \citet{salinas_2016}
